R Notebook

### 2022-11-17 Scripts/data_cleaning.Rmd
Working to build a v3 draft that highlights MM data

nelda <- nelda %>% mutate(first.mp.election = ifelse(first.mp.election == "yes", 1, ifelse(first.mp.election == "no", 0, NA)))
nelda <- nelda %>% mutate(protests = ifelse(protests == "yes", 1, ifelse(protests == "no", 0, NA)))
nelda <- nelda %>% mutate(inc.fav.cancel = ifelse(inc.fav.cancel == "yes", 1, ifelse(inc.fav.cancel == "no", 0, NA)))
nelda <- nelda %>% mutate(inc.fav.cancel.protests = ifelse(nelda35 == "yes", 1, 0))
nelda <- nelda %>% mutate(opp.fav.cancel = ifelse(nelda32 == "yes", 1, 0))
nelda <- nelda %>% mutate(inc.lose = ifelse(inc.lose == "yes", 1, ifelse(inc.lose == "no", 0, NA)))

>>>>

nelda <- nelda %>% mutate(elections.cancel.prot = ifelse(is.na(new.elections.held)==T, NA, ifelse(nelda35 == "yes" & new.elections.held == "yes", 1, 0)))
nelda <- nelda %>% mutate(first.mp.election = ifelse(first.mp.election == "yes", 1, ifelse(first.mp.election == "no", 0, NA)))
nelda <- nelda %>% mutate(protests = ifelse(protests == "yes", 1, ifelse(protests == "no", 0, NA)))
nelda <- nelda %>% mutate(inc.fav.cancel = ifelse(inc.fav.cancel == "yes", 1, ifelse(inc.fav.cancel == "no", 0, NA)))
nelda <- nelda %>% mutate(inc.fav.cancel.protests = ifelse(nelda35 == "yes", 1, 0))
nelda <- nelda %>% mutate(opp.fav.cancel = ifelse(nelda32 == "yes", 1, 0))
nelda <- nelda %>% mutate(inc.lose = ifelse(inc.lose == "yes", 1, ifelse(inc.lose == "no", 0, NA)))
